Exploring Homicide Trends in Toronto: A Seventeen-Year Statistical Overview (2004-2020)

### 2024-01-19 outputs/paper/paper.qmd
code fix
Grammatical errors fixed

```{r}
library("janitor")
library("tidyverse")
library("knitr")
```

@@

In addressing this need, the study utilizes a robust dataset from OpenDataToronto, specifically the “Police Annual Statistical Report - Homicides,” published by the Toronto Police Services. This dataset provides a detailed account of all recorded homicides under the jurisdiction of the Toronto Police Services over a seventeen-year period. Our research offers a meticulous examination of both the spatial distribution of homicides across Toronto's neighbourhoods and the methods used in these violent acts. The analysis, conducted through the R programming language and supplemented with various analytical tools like Tidyverse, Janitor, and Knitr, delves deep into the trends, revealing patterns that could have implications for policy formulation and implementation.

@@

The structure of the paper is as follows: Section 2 details the data sources, variables of interest, and the data processing techniques employed in the study. Section 2.2 is devoted to presenting and discussing the key findings, including yearly homicide trends, the geographical distribution of these incidents, and the analysis of the prevalent methods of homicide. The concluding section synthesizes these insights, drawing out their implications for urban policy, community safety strategies, and the broader societal understanding of urban violence in Toronto. This study not only sheds light on the current state of urban homicides in Toronto but also sets the stage for future research and policy development in this critical area.

>>>>

@@

In addressing this need, the study utilizes a robust dataset from OpenDataToronto [@opendatatoronto], specifically the “Police Annual Statistical Report - Homicides,” published by the Toronto Police Services. This dataset provides a detailed account of all recorded homicides under the jurisdiction of the Toronto Police Services over a seventeen-year period. Our research offers a meticulous examination of both the spatial distribution of homicides across Toronto's neighbourhoods and the methods used in these violent acts. The analysis, conducted through the R programming language [@R] and supplemented with various analytical tools like Tidyverse [@tidyverse], Janitor [@janitor], and Knitr [@knitr], delves deep into the trends, revealing patterns that could have implications for policy formulation and implementation.

@@

The structure of the paper is as follows: the data section details the data processing techniques employed in the study, afterwards is a brief discussion of the data set, followed by insight into the variables of interest. The analysis begins with the Yearly Homicide Trends section and is devoted to presenting and discussing the key findings, including yearly homicide numbers and trends, the geographical distribution of these incidents, and the analysis of the prevalent methods of homicide. The concluding section synthesizes these insights, drawing out their implications for urban policy, community safety strategies, and the broader societal understanding of urban violence in Toronto. This study not only sheds light on the current state of urban homicides in Toronto but also sets the stage for future research and policy development in this critical area.
